---
title: 'Peer-graded Assignment: Prediction Assignment Writeup'
output:
  html_document:
    fig_height: 4
    highlight: pygments
    theme: spacelab
  pdf_document: default
---
* * *

### Background
Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. These type of devices are part of the quantified self movement - a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it. In this project, your goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. More information is available from the website here: http://web.archive.org/web/20161224072740/http:/groupware.les.inf.puc-rio.br/har (see the section on the Weight Lifting Exercise Dataset).

### Data
The training data for this project are available here:

https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv

The test data are available here:

https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv

### Loading Library
This part load the library needed in this report.
```{r, message=FALSE, warning=FALSE}
library(caret)
library(rpart)
library(rpart.plot)
library(randomForest)
```

### Data preprocessing
This part preprocess the data as explained in the comments.
```{r}
## Read files
train <- read.csv("pml-training.csv", na.strings=c("NA","#DIV/0!", ""))
test <- read.csv("pml-testing.csv", na.strings=c("NA","#DIV/0!", ""))

## Remove columns with NAs
train <- train[, colSums(is.na(train)) == 0]
test <- test[, colSums(is.na(test)) == 0]

## Remove irrelevant columns
train <- train[, -c(1:7)]
test <- test[, -c(1:7)]
```


### Cross-validation
We divide the data into train and test set with a ratio of 75:25.
```{r}
sub <- createDataPartition(y=train$classe, p=0.75, list=FALSE)
subTrain <- train[sub, ]
subTest <- train[-sub, ]
```

### Prediction 1: Decision Tree
We first try to fit data with simple decision tree and plot its structure.
```{r}
model1 <- rpart(classe ~ ., data=subTrain, method="class")
rpart.plot(model1)
```

Then, we predict the data in the test set and analyze its accuracy.
```{r}
predict1 <- predict(model1, subTest, type = "class")
confusionMatrix(predict1, subTest$classe)
```
As we can see, we obtained the accuracy of 0.73 with the 95% confidence interval = (0.7122, 0.7374).

### Prediction 2: Random Forest
In this section, we try a more compliated model which is the random forest.
```{r}
model2 <- randomForest(classe ~ ., data=subTrain, method = "class")
```

```{r}
predict2 <- predict(model2, subTest, type = "class")
confusionMatrix(predict2, subTest$classe)
```
We can get a much better accuracy which is 0.99 with 95% confidence interval = (0.9937, 0.9975). The expected out-of-sample error is estimated at 0.05%. Therefore, the random forest is choosen in this study because of its accuracy even though the interpretability may be decreased.

### Quiz
This section generate the answer for the quiz portion.
```{r}
predict(model2, test, type="class")
```

* * *
